Adopting agile in the large: motivations, success factors and challenges

### 2014-04-28 journal/article.tex
Old work and commitments

@@

% General -->

>>>>

% Old work and commitments

A condition hindering the transformation was that old commitments still needed
to be tended to even though the organization was being restructured.
Some organizations started their agile journey in a state where people were
overcommitted, but it was later realized that overloaded people will not be able
to learn new ways of working and changing their behavior [P37, P42]. Cowan
describes how time was allocated for tending to old commitments [P11]. However,
even when extra work was prepared for people with specific expertise
became overloaded. After time it was realized that overcommitment must be
reduced by allowing to shift excess work for later time [P11]. In one case
people were forced to remain committed to firm deadlines which resulted in
ignoring new practices introduced by agile, and eventually in the agile method
breaking down.

@@
